---
title: "ForCatsPackageTutorial"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


## Dealing with Catergorical Data

Categoical variables deal with qualitative data and have have an infinite number or values vereses quantitative data that is on a continuious scale. 

(i.e. hair color, location, ethncity)

Although this information is useful, it might be hard to work with. Using a package to organize and manipulate categorical data can help.

###Packages to Work with Categorical Data

Forcats is a package under the Tidyverse universe. However, it is not one of the main packages so you would need to install forcats from tidyverse

You can install the package a few different way. 

Install the **forcats** package from [Github](https://github.com/tidyverse/forcats):

Or enter the r code listed below 

```{r, eval=FALSE}
devtools::install_github("tidyverse/forcats")
install.packages("forcats")
library(forcats)
```
## The Different Functions of Forcats

###1. Recoding a Factor

If you have categorical variables/factors, you can change the name or identity of that factor.

Use the fct_recode() 
```{r}
#Using data in r (airquality)
library(dplyr)
library(forcats)

# Take a look at the data
glimpse(airquality)

# The column month is listed as an integer so lets change it to a factor
airquality$Month <- factor(airquality$Month)

levels(airquality$Month)

# Now we can recode the factors into the categorical names of the months

airquality$Month <- fct_recode(airquality$Month, May = '5', June = '6', July = '7', Aug = '8', Sept = '9')

glimpse(airquality$Month)
```
###2. Reversing the order of the Factors

If you have categorical variables/factors in one order you can reverse that order.

Use fct_rev
```{r}

```




[link to factors reference](https://r4ds.had.co.nz/factors.html)
https://rpubs.com/tictacjoe/forcats_tutorial
https://forcats.tidyverse.org/articles/forcats.html
