---
title: "ForCatsPackageTutorial"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


## Dealing with Catergorical Data

Categoical variables deal with qualitative data and have have an infinite number or values vereses quantitative data that is on a continuious scale. 

(i.e. hair color, location, ethncity)

Although this information is useful, it might be hard to work with. Using a package to organize and manipulate categorical data can help.

###Packages to Work with Categorical Data


Forcats is a package under the Tidyverse universe.

-This type of package is relevant for categorical data. Such as 
First you need to install the package into your rstudio account

```{r}
library(forcats)
```

[link to factors reference](https://r4ds.had.co.nz/factors.html)
https://rpubs.com/tictacjoe/forcats_tutorial
https://forcats.tidyverse.org/articles/forcats.html
