---
title: "R Basic Problems"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
## Easy Practice Problems for Week 1

### Problem 1
Do simple math with numbers
```{r}

1+1
7-3
3*8
10/2

```
### Problem 2
Put numbers into variables-then do simple math
```{r}
AV<-3
C<-2
D<-4

AV+C
D-AV
C*D
D/C
```
###Problem 3
Place numbers 1-100 seperately 
```{r}
for(i in 1:100){
  print(i)
}
seq(1:100)
```
###Problem 4
Find sum of all intergers 1-100
```{r}
Vec<-(1:100)
sum(Vec)

```
###Problem 4.2
Summing using For Loop
```{r}
Numbers<-c()
Sum<-0
for (i in 1:100){
  if(i%%1==0){
    Numbers<-c(Numbers,i)
    Sum<-Sum+i
    
  }
}

 print(Sum) 
```
###Problem 5
Make your on summing function
```{r}
Sumfun<-function(a){
  total<-0
  for(i in a){
    total<-total+i
  }
return(total)
}

TestRun<-(1:3)
Sumfun(TestRun)

```
###Problem 6
List odd numbers from 1-100
```{r}
Oddnumbers<-c()
  seq(1,99,2)
```
###Problem 7
Prime numbers 1-1000
```{r}
Primenum<-c()
for(i in 1:1000)
  if(i%%2==0){
  print("Non Prime")
    }else if(i%%2==1){
  print("Prime")}

return(Primenum)


  
  
```

###Problem 8
100 random numbers
```{r}
runif(100)
```
###Problem 9
100 random numbers within range
```{r}
runif(100,min=1,max=20.5)
```
###Problem 10
Creating functions for descriptive statistics

Mean
```{r}
Average<-function(x){
  return(sum(x)/length(x))
}
Test<-(1:5)
Average(Test)
```
Mode
```{r}
Mode_A<-function(x){
  B<-table(x)
  which.max(B)
  print(names(which.max(B)))
        
}
Mtest<-c(1, 2 , 3 , 3 , 3 , 3 , 4 , 4 , 5 , 6 , 6 , 6)
Mode_A(Mtest)
```

Range
```{r}
Range_A<-function(x){
  return(max(x)-min(x))
}
Test3<-(1:10)
Range_A(Test3)
```
Median
```{r}
Middle<-function(x){
sort(x, decreasing = FALSE)
  B<-length(x)
  return(median(x))
}

test<-c(19,1,7,2,18,4)
Middle(test)
```

### Problem 11
Number of characters in a string
```{r}
Vec<-"AngelinaVasquez"
strsplit(Vec,split="")
```
### Problem 12
Number of words in string
```{r}
Sentence<-"How is your day ?"
sapply(strsplit(Sentence," "), length)

```
### Problem 13
Number of sentences in string
```{r}
Sent<-" Hello. It is nice today. The weather is sunny."
table(unlist(strsplit(Sent,split="[.]")))

```
###Problem 14
Number of times letter occurs in string
```{r}
B<- " My name is Angelina"
table(unlist(strsplit(B,split="")))

```
###Problem 15
Is a word in this sentence?
```{r}
A<-"Hi"
B<-"Hi there"
C<-"There is a cat"
D<-"The cat is in the tree"

grepl(A, B)

```
###Problem 16
Current time in milliseconds
```{r}
print(as.numeric(Sys.time())*1000, digits=15)
```


###Problem 17

###Problem 18

###Problem 19

###Problem 20
20x20 Matrix
```{r}

Mat<-matrix(runif(10),ncol=20,nrow=20)
print(Mat)
```

###Problem 21
