---
title: "R Intrinsics"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
This is a page that lists functions and has a brief description of how they work.

##Assignment Number 2

###General functions
1.
Help(topic)

2.
?topic

This function is used when you are looking for the help page documentation of a certain topic in R.
For example you want to understand the summing function
```{r}
?sum
```
3.
Is()

This function is used to see if a certain object in R is part of a class you selected. This is a logical statement.If it is in the class or if it is not in the class then True or False will be returned
```{r}
is
```
4.
dir()

This function is used to create a vector of characters for a name of files or folders in a directory

5.
list.files()

Similar to the dir function, this function creates a vector of the names of files or folders in a directory

###Input and Output
1.
save()

This function is used to create a temporary file to show that you saved your current word




