---
title: "R Intrinsics"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
This is a page that lists functions and has a brief description of how they work.

##Assignment Number 2

###General functions
1.
Help(topic)

This function shows you all the help systems for a problem
```{r}
help(sum)
```


2.
?topic

This function is used when you are looking for the help page documentation of a certain topic in R.
For example you want to understand the summing function
```{r}
?sum
```
3.
Is()

This function is used to see if a certain object in R is part of a class you selected. This is a logical statement.If it is in the class or if it is not in the class then True or False will be returned
```{r}
A<-"H"
is(A, "character")
```
4.
dir()

This function is used to create a vector of characters for a name of files or folders in a directory
```{r}
A<-"hello"
dir(A)
```

5.
list.files()

Similar to the dir function, this function creates a vector of the names of files or folders in a directory

###Input and Output
1.
save()

This function is used to create a temporary file to show that you saved your current work.
```{r}
save

```


2.
load()

This is used to reload what you previously saved with the save func

3.
data()

This function loads the data sets you have
```{r}
A<-c(1,2,3)
B<-c(5,6,7)
data(A,B)
```


4.
library()

This function loads, attaches, and lists packages


5.
read.csv()

This function transposes a data table to a data frame.

6.
read.table()

Similar to  the previous function this reads table data and creates a data frame 

7. 
scan()

Reads data in a vector or list

8.
print()

This function prints out the argument
```{r}
A<-1
B<-2
print(sum(A,B))

```


9.
cat()

This concatenates outputs of objects

10. 
write.table()


This prints an arguement after its converted from a data frame



