---
title: "R Intrinsics"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
This is a page that lists functions and has a brief description of how they work.

##Assignment Number 2

###General functions
1.
Help(topic)

This function shows you all the help systems for a problem
2.
?topic

This function is used when you are looking for the help page documentation of a certain topic in R.
For example you want to understand the summing function
```{r}
?sum
```
3.
Is()

This function is used to see if a certain object in R is part of a class you selected. This is a logical statement.If it is in the class or if it is not in the class then True or False will be returned
```{r}
is
```
4.
dir()

This function is used to create a vector of characters for a name of files or folders in a directory

5.
list.files()

Similar to the dir function, this function creates a vector of the names of files or folders in a directory

###Input and Output
1.
save()

This function is used to create a temporary file to show that you saved your current work.

2.
load()

This is used to reload what you previously saved with the save func
3.
data()

This function loads the data sets you have

4.
library()

This function loads, attaches, and lists packages


5.
read.csv()

This function transposes a data table to a data frame.

6.
read.table()

Similar to  the previous function this reads table data and creates a data frame 

7. 
scan()

Reads data in a vector or list

8.
print()

This function prints out the argument

9.
cat()

This concatenates outputs of objects

10. 
write.table()


This prints an arguement after its converted from a data frame



